Niche complementarity between pollinators increases community-level plant reproductive success

### 2019-08-08 paper_round2.Rmd
Redo sorensen
pequeños cambios

Within each site, we marked between 3 and `r max(f.inds$tot.inds)` individuals (mean $\pm$ SD: `r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`) belonging to `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (mean $\pm$ SD:`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`), depending on the availability and presence of flowers during the sampling events. For each individual, at the end of the season, we 
recorded fruit set (i.e. the proportion of flowers that set fruit), the average number of seeds per fruit and the average fruit and seed weight per fruit (`r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits subsampled, mean $\pm$ SD: `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`). Our survey included a total of `r nlevels(f2$Plant.sp)` different plant species across our `r nlevels(f2$Site_ID)` sites. Plants species were selected based on their availability, with sampling being focused on the most abundant plant species. The values at the species level were then averaged per site to calculate unique reproductive success measures at the site level. [X % of the plant species depend on pollinators to maximize their reproduction (Table SX).]()

@@

  All of these metrics were calculated using all the data as well as for the subset of the data excluding interactions observed outside of sampling periods. Differences between results are minimal for both and thus we will only present results for the analysis using the full dataset (see Table S11A-H for results removing observations out of transect).

@@

# extract estimates and st error for m1 and present them in paper
tableS4<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2)
rownames(tableS4)<-c("(Intercept)", "Pollinator richness", "Total number of visits")

@@

# extract estimates and st error for m2 and present them in paper
tableS5<-round(summary(m2.fruit.w)$coefficients$cond[,1:3], digits=2)
rownames(tableS5)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Plant niche overlap")

```
 For all other measures of reproductive success considered (i.e., fruit and seed weight), both models had very similar fits, with ($\Delta AIC=2.2$) and 2, respectively. However, none of the variables included within our model explain the differences observed (Tables S4-S5).

@@

At the site level, we find different patterns for fruit set and the number of seeds per fruit as compared to those for fruit and seed weight. In the case of fruit set and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed when penalizing for model complexity (i.e.,$\Delta AIC<2$; [@Burnham2002]). This suggests model 2 is a good model despite its added complexity, and actually shows a substantially better predictive ability than model 1 (R^2 = `r round(r2.m2, 2)` for model 2 versus `r round(r2.m1, 2)` for model 1 in the case of fruit set and R^2 = `r round(r2.m2.seed,2)` for model 2 versus `r round(r2.m1.seed, 2)` for model 1 in the case of the number of seeds per fruit) and therefore we will comment results for this model only. In particular, we find that both fruit set and the number of seeds per fruit are positively related to niche complementarity between pollinators (Tables 2, Fig. 3). Additionally, we find a negative effect of site-level pollinator richness on average fruit set (Table 2A, Fig. 3).

@@

#save table with results for paper
tableS6<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)
rownames(tableS6)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper

@@

#save table with results for paper
tableS7<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)
rownames(tableS7) <-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper

@@

  Contrastingly, in the case of weight variables (fruit and seed weight), in both cases we find that the best model is model 1, i.e., that only including simple visitation metrics (R^2 = `r round(r2.fruitw1[2], 2)` in the case of fruit weight and `r round(r2.seedw1[2], 2)` in the case of seed weight). Here, we find a consistent positive effect of site-level pollinator richness for both weight descriptors (Tables S6-S7, Fig. 4).

@@

When evaluating the effect of differences in community composition and network structure for equity in reproductive success across the different species within a community we find that model 1 is the best model for all the thresholds considered (50^th, 25^th and 75^th percentiles). Here, none of the variables considered are able to explain differences observed in equity across sites (Tables S8, S9, S10).

@@

#save table with results for paper, both models are equally good so save both tables
tableS8<-round(summary(m1.eq.comm)$coef[,1:3], digits=2)
rownames(tableS8)<-c("(Intercept)", "Pollinator richness", "Total number of visits")

@@

tableS9<-round(summary(m1.eq.comm75)$coef[,1:3], digits=2)
rownames(tableS9)<-c("(Intercept)", "Pollinator richness", "Total number of visits")

@@

tableS10<-round(summary(m1.eq.comm25)$coef[,1:3], digits=2)
rownames(tableS10)<-c("(Intercept)", "Pollinator richness", "Total number of visits")

@@

tableS4<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2)
rownames(tableS4)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
kable(tableS4, caption="Table S4. Results of GLMM showing effect of simple visitation metrics on species-level average seed weight based on best model selected.")

tableS5<-round(summary(m1.fruit.w)$coefficients$cond[,1:3], digits=2)
rownames(tableS5)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
kable(tableS5, caption="Table S5. Results of GLMM showing effect of simple visitation metrics on species-level average fruit weight based on best model selected.")
```

@@

tableS6<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)
rownames(tableS6)<-c("(Intercept)", "Pollinator richness", "Total number of visits")

kable(tableS6, caption="Table S6. Results of GLM showing effect of simple visitation metrics on site-level average fruit weight based on best model selected.")
```

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
#save table with results for paper
tableS7<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)
rownames(tableS7) <-c("(Intercept)", "Pollinator richness", "Total number of visits")

kable(tableS7, caption="Table S7. Results of GLM showing effect of simple visitation metrics on site-level average seed weight based on best model selected.")
```

@@

kable(tableS8, caption="Table S8. Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a site based on best model selected (0.50 threshold).")

kable(tableS9, caption="Table S9. Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a site based on best model selected (0.75 threshold).")

kable(tableS10, caption="Table S10. Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a site based on best model selected (0.25 threshold).")
```

>>>>

Within each site, we marked between 3 and `r max(f.inds$tot.inds)` individuals (mean $\pm$ SD: `r round(mean(f.inds$tot.inds), digits=2)` $\pm$ `r round(sd(f.inds$tot.inds), digits=2)`, Table S2) belonging to `r min(tableS1$tot.sps)` to `r max(tableS1$tot.sps)` plant species (mean $\pm$ SD:`r round(mean(tableS1$tot.sps), digits=2)` $\pm$ `r round(sd(tableS1$tot.sps), digits=2)`, Table S1), depending on the availability and presence of flowers during the sampling events. For each individual, at the end of the season, we 
recorded fruit set (i.e. the proportion of flowers that set fruit), the average number of seeds per fruit and the average fruit and seed weight per fruit (`r min(s.fruitnum$tot.fruits)`-`r max(s.fruitnum$tot.fruits)` fruits subsampled, mean $\pm$ SD: `r round(mean(s.fruitnum$tot.fruits), digits=2)` $\pm$ `r round(sd(s.fruitnum$tot.fruits), digits=2)`, Table S3). Our survey included a total of `r nlevels(f2$Plant.sp)` different plant species across our `r nlevels(f2$Site_ID)` sites. Plants species were selected based on their availability, with sampling being focused on the most abundant plant species. The values at the species level were then averaged per site to calculate unique reproductive success measures at the site level. 68% of the plant species depend on pollinators to maximize their reproduction (Table S4).

@@

  All of these metrics were calculated using all the data as well as for the subset of the data excluding interactions observed outside of sampling periods. Differences between results are minimal for both and thus we will only present results for the analysis using the full dataset (see Table S12A-H for results removing observations out of transect).

@@

# extract estimates and st error for m1 and present them in paper
tableS5<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2) #ch
rownames(tableS5)<-c("(Intercept)", "Pollinator richness", "Total number of visits")

@@

# extract estimates and st error for m2 and present them in paper
tableS6<-round(summary(m2.fruit.w)$coefficients$cond[,1:3], digits=2)#ch
rownames(tableS6)<-c("(Intercept)", "Pollinator richness", "Total number of visits", "Centrality", "Plant niche overlap")

```
 For all other measures of reproductive success considered (i.e., fruit and seed weight), both models had very similar fits, with ($\Delta AIC=2.2$) and 2, respectively. However, none of the variables included within our model explain the differences observed (Tables S5-S6).

@@

At the site level, we find different patterns for fruit set and the number of seeds per fruit as compared to those for fruit and seed weight. In the case of fruit set and the number of seeds per fruit, we find that both model 1 and 2 are equally good in describing the differences observed when penalizing for model complexity (i.e.,$\Delta AIC<2$; [@Burnham2002a]). This suggests model 2 is a good model despite its added complexity, and actually shows a substantially better predictive ability than model 1 (R^2 = `r round(r2.m2, 2)` for model 2 versus `r round(r2.m1, 2)` for model 1 in the case of fruit set and R^2 = `r round(r2.m2.seed,2)` for model 2 versus `r round(r2.m1.seed, 2)` for model 1 in the case of the number of seeds per fruit) and therefore we will comment results for this model only. In particular, we find that both fruit set and the number of seeds per fruit are positively related to niche complementarity between pollinators (Tables 2, Fig. 3). Additionally, we find a negative effect of site-level pollinator richness on average fruit set (Table 2A, Fig. 3).

@@

#save table with results for paper
tableS7<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)#ch
rownames(tableS7)<-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper

@@

#save table with results for paper
tableS8<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)#ch
rownames(tableS8) <-c("(Intercept)", "Pollinator species diversity", "Total number of visits")#end of paper

@@

  Contrastingly, in the case of weight variables (fruit and seed weight), in both cases we find that the best model is model 1, i.e., that only including simple visitation metrics (R^2 = `r round(r2.fruitw1[2], 2)` in the case of fruit weight and `r round(r2.seedw1[2], 2)` in the case of seed weight). Here, we find a consistent positive effect of site-level pollinator richness for both weight descriptors (Tables S7-S8, Fig. 4).

@@

When evaluating the effect of differences in community composition and network structure for equity in reproductive success across the different species within a community we find that model 1 is the best model for all the thresholds considered (50^th, 25^th and 75^th percentiles). Here, none of the variables considered are able to explain differences observed in equity across sites (Tables S9, S10, S11).

@@

#save table with results for paper, both models are equally good so save both tables
tableS9<-round(summary(m1.eq.comm)$coef[,1:3], digits=2)#ch
rownames(tableS9)<-c("(Intercept)", "Pollinator richness", "Total number of visits")

@@

tableS10<-round(summary(m1.eq.comm75)$coef[,1:3], digits=2)#ch
rownames(tableS10)<-c("(Intercept)", "Pollinator richness", "Total number of visits")

@@

tableS11<-round(summary(m1.eq.comm25)$coef[,1:3], digits=2)#ch
rownames(tableS11)<-c("(Intercept)", "Pollinator richness", "Total number of visits")

@@

tableS5<-round(summary(m1.seed.w)$coefficients$cond[,1:3], digits=2)
rownames(tableS5)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
kable(tableS5, caption="Table S5. Results of GLMM showing effect of simple visitation metrics on species-level average seed weight based on best model selected.")

tableS6<-round(summary(m1.fruit.w)$coefficients$cond[,1:3], digits=2)
rownames(tableS6)<-c("(Intercept)", "Pollinator richness", "Total number of visits")
kable(tableS6, caption="Table S6. Results of GLMM showing effect of simple visitation metrics on species-level average fruit weight based on best model selected.")
```

@@

tableS7<-round(summary(m1.fruitw.net)$coef[,1:3], digits=2)
rownames(tableS7)<-c("(Intercept)", "Pollinator richness", "Total number of visits")

kable(tableS7, caption="Table S7. Results of GLM showing effect of simple visitation metrics on site-level average fruit weight based on best model selected.")
```

```{r, include=TRUE, echo = FALSE, message=FALSE, error=FALSE, warning=FALSE, fig.height=5}
#save table with results for paper
tableS8<-round(summary(m1.seedw.net)$coef[,1:3], digits=2)
rownames(tableS8) <-c("(Intercept)", "Pollinator richness", "Total number of visits")

kable(tableS8, caption="Table S8. Results of GLM showing effect of simple visitation metrics on site-level average seed weight based on best model selected.")
```

@@

kable(tableS9, caption="Table S9. Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a site based on best model selected (0.50 threshold).")

kable(tableS10, caption="Table S10. Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a site based on best model selected (0.75 threshold).")

kable(tableS11, caption="Table S11. Results of GLM showing effect of simple visitation metrics on equity in reproductive success across plant species within a site based on best model selected (0.25 threshold).")
```
